---
title: "HWK1"
author: "LeTicia Cancel"
date: "8/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Intro

The data for this assignment is from the lastest Governor Polls data found on the [FiveThirtyEight](https://data.fivethirtyeight.com/) site. 


### Load libraries
```{r, error=FALSE, warning=FALSE}
#install.packages("RCurl")
library(RCurl)
library(ggplot2)
```

### Load Governors Polls Data from GitHub and create a dataframe 
```{r}
x <- getURL("https://raw.githubusercontent.com/ltcancel/DATA607_HWK1/master/Week1/polls/governor_polls.csv")

df <- read.csv(text = x)

head(df)
```

# Conclusion

I would use bar charts to explore this data starting with a count of candidates based on party (example below). Since there is a low count for most of the candidate parties, I would investigate the top 5 parties and break down who makes up the top 5 parties. 

```{r}
ggplot(df) +
  geom_bar(mapping = aes(x = candidate_party)) +
  coord_flip()
```

The method of voting would also be an interesting data point to explore. 

```{r}
ggplot(df) +
  geom_bar(mapping = aes(x = methodology)) +
  coord_flip()
```

